### 2021-10-02 docs/paper/sections/1_introduction.tex
Prove bad consequences of knowledge deficits in introduction

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}. \TODO{do we need to prove each of this?}
Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

>>>>

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces \citep{piccioni2013empirical}, unidentified defects \citep{wong2017more}, and compatibility problems \citep{bogart2015breaks}.
Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.
